Exploring the Impact of Queer Media Characters on LGBTQ+ Psychological Well-Being: The Role of Queer Media Consumption, Perceived Authenticity, and Intersectionality

### 2025-02-18 Queer Characters and LGBTQ+ Well-being.qmd
Dingning Yang - Project submission #2 for grading - @nrdowling @Regenchen

  | This study contributes to a more nuanced understanding of LGBTQ+ individuals' diverse needs and experiences with queer media representation, which has significant implications for media producers, mental health professionals, and LGBTQ+ advocacy groups in fostering more positive and inclusive media representations for the LGBTQ+ community.
keywords: [LGBTQ+ well-being, queer media representations, intersectionality]
floatsintext: true
format:
  apaquarto-pdf:
    csl: apa.csl
    documentmode: man
    indent: true
    include-in-header: 
      text: |
        \usepackage{setspace}
        \linespread{2}
        \renewcommand{\footnotesize}{\fontsize{8}{10}\selectfont}
bibliography: References.bib

@@

```{r}
#| label: setup
#| include: false
# Install required packages
if(!require(tidyverse)){install.packages("tidyverse")}
if(!require(ggplot2)){install.packages("ggplot2")}
if(!require(psych)){install.packages("psych")}
if(!require(knitr)){install.packages("knitr")}
if(!require(kableExtra)){install.packages("kableExtra")}

# List of required packages
required_packages <- c ("tidyverse", "ggplot2", "psych","knitr", "kableExtra")

>>>>

  | This study contributes to a more nuanced understanding of LGBTQ+ individuals' diverse needs and experiences with queer media representation, which has significant implications for media producers, mental health professionals, and LGBTQ+ advocacy groups in fostering more positive and inclusive media representations for the LGBTQ+ community.
keywords: [LGBTQ+ well-being, queer media representations, intersectionality]
floatsintext: true
format:
  apaquarto-pdf:
    documentmode: man
    indent: true
    include-in-header: 
      text: |
        \usepackage{setspace}
        \linespread{2}
        \renewcommand{\footnotesize}{\fontsize{8}{10}\selectfont}
bibliography: References.bib

@@

```{r}
#| label: setup
#| include: false
# Install required packages
if(!require(tidyverse)){install.packages("tidyverse")}
if(!require(ggplot2)){install.packages("ggplot2")}
if(!require(ggiraph)){install.packages("ggiraph")}
if(!require(RColorBrewer)){install.packages("RColorBrewer")}
if(!require(viridis)){install.packages("viridis")}
if(!require(maps)){install.packages("maps")}
if(!require(mapdata)){install.packages("mapdata")}
if(!require(gridExtra)){install.packages("gridExtra")}
if(!require(plotly)){install.packages("plotly")}
if(!require(wordcloud2)){install.packages("wordcloud2")}
if(!require(shiny)){install.packages("shiny")}
if(!require(psych)){install.packages("psych")}
if(!require(knitr)){install.packages("knitr")}
if(!require(kableExtra)){install.packages("kableExtra")}

# List of required packages
required_packages <- c ("tidyverse", "ggplot2", "ggiraph", "RColorBrewer", "viridis", "maps", "mapdata","gridExtra", "plotly", "wordcloud2", "shiny", "psych","knitr", "kableExtra")
